\subsection{Flutter Plugins and Packages}
The Flutter Framework is a cross-platform development framework that was released by Google in 2018. Flutter uses the Dart programming language and makes it possible to write a codebase purely in Dart, and compiling this code to native iOS and Android code. What this means is that an application developer can create an application for both platforms with a single codebase. However whenever native-specific APIs have to be invoked such as that of the camera or various phone-sensors, a package developer has to write a library that does so, by means of a method invocation from the Dart language which triggers the corresponding API invocation ob the Android or iOS platform. This method invocation library is referred to as a \textit{plugin} within the Flutter world, in contrast to a \textit{package} which simply invokes other Dart code and as such contains no platform-specific source code. The \textit{Mobility Features Package} will be a Flutter package that contains a collection of algorithms that provides an application programmer with object-oriented abstractions that allows him/her to calculate relevant features for a mobile health application. The Location API, available on both iOS and Android, will not be invoked directly from this package since that would require it to be a plugin. This has two main upsides: From the point of the application developer, it allows him/her to use their location plugin of choice (of which there are many \footnote{\url{https://pub.dev/packages?q=location}} with specific parameters for how the location is tracked (ex frequency and distance). Secondly, from the perspective of the maintainer of this package, the package becomes much more modular and in turn easier to maintain.