\section{Goals and Methods}
% While the above section details the problems, your job is to then translate those problems into research goals. Each goal should briefly indicate how you are going to solve the problem i.e., the method you will use to solve it. Note that some authors sometimes combine problem statements/goals/methods into a single section, while others separate it. Goals should be operational, i.e., if you later claim to achieve your goal, you should be able to match your solution against the goal statement.

% I cannot overstate how important it is to have clear goals. Most examiners highlight these goals, and after reading the thesis they then go back to see if you have actually accomplished your goals. If you have not, then you have a big problem with your thesis. Even worse are theses where problems and goals are not clearly stated, for it means people are trying to evaluate your solutions in a vacuum.

The research goals closely match the research questions and will explain how the different sub-questions are answered, and which methods are used to do so.

\subsubsection*{Goal 1: Implement the Off-line Mobility Feature Algorithms}
Saeb et al. \cite{Saeb2015} describes a list of mobility features, some of which they prove to strongly correlate with depressive behavior. These features need to be implemented in their most simple form, i.e. off-line, where all the location data for a given day is readily available. This will be carried out in Python with a synthetic dataset and later in Dart. This is done in order to demonstrate the quality of the algorithms. A pre-processing procedure inspired by Cuttone et al. \cite{sparse-location-2014} for finding certain features has been implemented by Jonas Busk prior to starting this thesis. 

\subsubsection*{Goal 2: Adapt Algorithms to Work in Real-time}
The features described above will be implemented such that they can be evaluated on a partial dataset, i.e. an incomplete day's data. Many of the features will have minor changes applied to their calculation, however, the \textit{Routine Index} feature as defined by Canzian et al.\cite{Canzian2015} and Saeb et al. \cite{Saeb2015} may prove to be a challenge to implement in real-time. By its definition, this feature lends itself to be computed only once multiple full days of data have been collected, making the feature non-trivial to implement in a real-time fashion where it may compute on a partial, incomplete dataset. 

\subsubsection*{Goal 3: Implement Real-time Mobility Features in Flutter}
An algorithm/procedure that runs the Mobility Feature algorithms on a smart-phone has to be written which involves a couple of steps. Location data has to be collected and stored on the smartphone, and then it has to be demonstrated that features can be computed whenever they need to be. However, storing raw data every day would end up taking up too much disk space and is therefore not an ideal solution when working with a smartphone. This means the solution has to be able to compute these history-dependent features without relying on storing raw data of each day.

\subsubsection*{Goal 4: Design a Flutter Software Package}
The software package should be designed according to the Flutter packages best practices \footnote{\url{flutter.dev/docs/development/packages-and-plugins/developing-packages}}, be properly documented and be released on the Dart package manager \footnote{\url{www.pub.dev}}.

\subsubsection*{Goal 5: Develop a Demo Mobile Application}
To demonstrate how the software package containing the algorithm will be used in practice, a Flutter demo-app will be developed in parallel with the software package. The functionality of the application should be in accordance with the contents of \textit{Goal 3}. By developing an actual application and seeing the algorithms in use, the structure of the API should emerge such that it is 'nice to use' from an application developer's point of view.

\subsubsection*{Goal 6: Conduct a Field Study}
To test the quality of the Mobility Features in action, a small scale study of 5-10 participants should be conducted and should run for 2-4 weeks (the longer the better). The participants will use the demo application. Also, in order to validate the quality of the features produced daily during these weeks, the participants will have to fill out a small diary in order to compare the results of the algorithms with the subjective experience of the users. This diary will be a part of the demo application. Preferably the users should be reminded daily to fill out the diary such that as much user data is collected as possible.

