\section{Results}
The Mobility Features Package was implemented in the Flutter framework and supports on-device real-time mobility feature computation. From the work of Saeb et al. \cite{Saeb2015} and Canzian et al. \cite{Canzian2015} the features \textit{Home Stay, Number of Places, Distance Travelled, Location Variance, Entropy, Normalized Entropy,} and \textit{Routine Index} were chosen to be included in the package. A set of additional location features, e.g. stops, places and moves, were included as well, inspired by the work of Cuttone et al. \cite{sparse-location-2014} and Canzian et al. \cite{Canzian2015}. Features are computed in real-time using historical stops and moves stored on the phone which lowers the storage requirements greatly compared to using raw location data for feature computation. The Mobility Features Package makes it possible for the application programmer to compute mobility features with just 3 lines of code. This comes as the result of the API concealing the feature implementation details from the programmer to very high degree. The package does not depend on any specific location plugin due to its design, which allows the programmer to flexibly choose their own plugin for tracking location data. This allows for easier maintenance and enables the package to be used among other packages dependent on location tracking, without causing dependency issues. The capabilities of the package was demonstrated through a field study with 10 participants lasting 3 weeks. For this study a Flutter application collected the participants' location and used the package to compute the participants' features multiple times daily. Participants also filled out a daily questionnaire pertaining to the features, which were compared to the computed features. In the 3-weeks study following insights concerning the Mobility package were drawn:

\begin{itemize}
    \item All the participants successfully installed and used the Mobility Features throughout the study period.
    
    \item Mobility features were computed several times a day, however, as in similar 'in the wild' studies, non-uniform gaps were observed in the collected location data, which reduced the accuracy of the computed features.
    
    \item When comparing the daily location features with subjective user data we found that the Mobility Features Package predicts the Number of Places visited with an RMSE of 0.5 places, the Home Stay percentage with an RMSE of 14.3\% and the Routine Index with an RMSE of 22.5\%.
    
    \item The algorithms tends to undershoot in predicting the number of places and home stay, likely due to gaps in the data. There is no consistent over- or undershooting done when it comes to computing the Routine Index, which likely stemmed from gaps in the location data, as well as variance the validity of the subjective answers regarding the participants routine.
\end{itemize}
