\section{Thesis Overview}

The process of developing the Mobility Features Package is documented in the following chapters for which a brief overview is given below.\\

\textbf{Chapter 2: Related Work} will outline a set of relevant contributions related to behaviour and mental state tracking through mobile sensing. \\

\textbf{Chapter 3: Theoretical Background} will describe all the theory behind computing the features. This includes definitions and discussion of all the features, as well as the algorithms that can extract mobility patterns from this data. The section is very mathematical as well as philosophical and lays the ground work for the later implementation.\\

\textbf{Chapter 4: Software Design} will discuss the design choices and principles used to model a software system capable of computing the mobility features. Design pertains to both how the internal system of the package works as well as the public facing API which is the interface the application programmer talks to when using the package.\\

\textbf{Chapter 5: Flutter Implementation} will describe how the domain model and the feature algorithms were implemented in the Dart language. How a user may use the final version of the package is also described.\\

\textbf{Chapter 6: Validation} will outline the field study that was conducted in which 10 participants. The participants were tracked with a mobile application that used the Mobility Features Package to compute daily features based on their location data. Implementation of the mobile application is also discussed in this chapter.\\

\textbf{Chapter 7: Results and Discussion} will include a data analysis of the study conducted in which the computed features are compared with the subjective answers given by participants. Additionally, further work is discussed which includes improvements to the package, the algorithms and concrete applications for the Mobility Features Package in the near future.\\

\textbf{Chapter 8: Conclusion} will report the major findings of the thesis and answer the research questions in detail.\\