\section{Digital Phenotyping}
Mobile sensing is the field of using the phone's sensors to collect data user data and can include predicting the user state from this data. Some applications of mobile sensing include mental health monitoring, for which different terms are used such as "digital phenotyping" and "context generation". Mobile sensing for mental healthcare has the potential of providing a practical and low-cost approach to deliver psychological interventions for the prevention of mental health disorders \cite{mobile-based-interventions} as well as bringing mental healthcare to populations that do not have access to traditional psychotherapy \cite{future-mental-health}. Within the context of mobile sensing for behaviour and mental state, location data is commonly used. The work by Insel \cite{digital_phenotyping} deals with the topic of collecting and aggregating user data into a so-called digital phenotype. It is predicted that by 2050, the biggest impact in psychiatry and mental health will have been the revolution in technology- and information science. Smartphones have become ubiquitous in the past decade and there are over three billion smartphones with a data plan worldwide, each of which has computing power which surpasses supercomputers of the 1990s. In areas around the world without access to resources such as clean water and food, ownership of a smartphone and access to information has become a symbol of modernity. In the realm of psychiatry, a current data collection problem is the dependence on self-reporting of sleep, appetite, and emotional state, even though it is recognized that depression will impair people's ability to remain objective in assessing their own behavior and thus data is prone to be faulty \cite{digital_phenotyping}. Another current problem is how people suffering from mental illness tend to not seek help before it is too late. Depressive relapses are therefore also often reported with considerable delay for patients currently in treatment. The smartphone offers an objective form of mental-state measurement which is referred to was \textit{Digital Phenotyping}, which uses built-in sensors such as geo-location, accelerometer, and human-computer interactions (HCI) to infer the state of the patient. This makes it possible to assess people by using data in a real-time fashion, rather than in retrospect as is currently is done. Digital phenotyping could in theory fill the role of a smoke detector which provides early signs of relapse and recovery, without replacing the face-to-face consultations entirely. In addition, this also allows researchers to track patients in their own environment, rather than in a clinical environment.

% Extraction of behavioural features
% Provides a list of mobility features discussed by SAEB
% Main idea of the paper is to provide a list of featues for different data channels
% By covering all data channels the less the chance of losing out on data

% Doryab et al. \cite{extraction-of-behavioural-features} proposes a method for extracting a series of behavioural features from multiple smartphone data channels with each channel resulting in a set of features. Examples of channels are GPS data, phone usage, step count, etc. The upside of having many channels is improved accuracy since more data is available to describe the behavior of the user which means having periods of no data at all becomes very unlikely. The authors describe how they used the \textit{AWARE Framework} \cite{aware2015} to collect data such as \textit{Bluetooth}, \textit{Call-log}, \textit{Location}, \textit{Campus Map}, \textit{Phone Usage}, \textit{Step Count} and \textit{Sleep State} (via FitBit).

% \begin{table}[]
%     \centering
% \begin{tabular}{|l|l|}
% \hline
% {\ul \textbf{Feature}}        & {\ul \textbf{Description}}                                                                                            \\ \hline
% Significant Places            & \textit{Location clusters for samples with a speed \textless 1 km/h}                                                  \\ \hline
% Location Variance             & \textit{A collection of location samples representing visit at a known place with an arrival and departure timestamp} \\ \hline
% Distance Travelled            & \textit{A cluster of stops found the DBSCAN algorithm}                                                                \\ \hline
% Average Speed                 & \textit{A travel between two stops with a path of location samples}                                                   \\ \hline
% Variance in Speed             & \textit{The number of places visited today}                                                                           \\ \hline
% Circadian Movement            & \textit{See Saeb et al.}                                                                                              \\ \hline
% Number of Significant Places  & \textit{The number or of}                                                                                             \\ \hline
% Number of Transitions         & \textit{Number of transitions between places}                                                                         \\ \hline
% Radius of Gyration            & \textit{The radius of the area covered}                                                                               \\ \hline
% Time Spent at Top 3 Places    & \textit{The percentage of time spent at the top 3 most significant places}                                            \\ \hline
% Percentage of Time Moving     & \textit{The percentage of the time with a speed \textgreater 1 km/h}                                                  \\ \hline
% Time at Ingsignificant Places & \textit{The percentage of time spent at places that are rarely visited}                                               \\ \hline
% Length of Stay at Clusters    & \textit{Statistics for the time spent at different clusters}                                                          \\ \hline
% Location Entropy              & \textit{See Saeb et al.}                                                                                              \\ \hline
% \end{tabular}
%     \caption{The Mobility Features defined by Doryab et a. \cite{extraction-of-behavioural-features}}
%     \label{tab:features-doryab}
% \end{table}